\section{Acknowledgments}

This research is part of the Blue Waters sustained-petascale computing project, 
which is supported by the National Science Foundation (awards OCI-0725070 and 
ACI-1238993) and the state of Illinois. Blue Waters is a joint effort of the 
University of Illinois at Urbana-Champaign and its National Center for 
Supercomputing Applications 

The authors would like to thank  members of the \gls{ARFC} group at the 
University of Illinois - Urbana Champaign who provided valuable code reviews 
and proofreading.

The authors contributed to this work as described below.  Andrei Rykhlevskii 
conceived and designed the simulations, wrote the paper, prepared figures 
and/or tables, performed the computation work, contributed to the software 
product, and reviewed drafts of the paper. Jin Whan Bae conceived and designed 
the simulations, wrote the paper, contributed to the software 
product, and reviewed drafts of the paper. Andrei Rykhlevskii 
is supported by 
DOE ARPA-E MEITNER program award 1798-1576. 
Jin Whan
Bae is supported by funding received from the DOE Nuclear Energy University
Program (Project 16-10512) `Demand-Driven Cycamore Archetypes'.

Kathryn D. Huff directed and 
supervised the work, conceived and designed the simulations, 
contributed to the software product, and reviewed drafts of the paper.  Prof. 
Huff is supported by the Nuclear Regulatory Commission Faculty Development 
Program, the National Center for Supercomputing Applications, the NNSA Office 
of Defense Nuclear Nonproliferation R\&D through the Consortium for Verfication 
Technologies and the Consortium for Nonproliferation Enabling Capabilities,  
the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), 
sponsored by the Japanese Ministry of Education, Culture, Sports, Science and 
Technology, and DOE ARPA-E MEITNER program award 1798-1576. 

