%        File: revise.tex
%     Created: Wed Oct 27 02:00 PM 2018 P
% Last Change: Wed Oct 27 02:00 PM 2018 P
%

%
% Copyright 2007, 2008, 2009 Elsevier Ltd
%
% This file is part of the 'Elsarticle Bundle'.
% ---------------------------------------------
%
% It may be distributed under the conditions of the LaTeX Project Public
% License, either version 1.2 of this license or (at your option) any
% later version.  The latest version of this license is in
%    http://www.latex-project.org/lppl.txt
% and version 1.2 or later is part of all distributions of LaTeX
% version 1999/12/01 or later.
%
% The list of all files belonging to the 'Elsarticle Bundle' is
% given in the file `manifest.txt'.
%

% Template article for Elsevier's document class `elsarticle'
% with numbered style bibliographic references
% SP 2008/03/01
%
%
%
% $Id: elsarticle-template-num.tex 4 2009-10-24 08:22:58Z rishi $
%
%
%\documentclass[preprint,12pt]{elsarticle}
\documentclass[answers,11pt]{exam}

% \documentclass[preprint,review,12pt]{elsarticle}

% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
% for a journal layout:
% \documentclass[final,1p,times]{elsarticle}
% \documentclass[final,1p,times,twocolumn]{elsarticle}
% \documentclass[final,3p,times]{elsarticle}
% \documentclass[final,3p,times,twocolumn]{elsarticle}
% \documentclass[final,5p,times]{elsarticle}
% \documentclass[final,5p,times,twocolumn]{elsarticle}

% if you use PostScript figures in your article
% use the graphics package for simple commands
% \usepackage{graphics}
% or use the graphicx package for more complicated commands
\usepackage{graphicx}
% or use the epsfig package if you prefer to use the old commands
% \usepackage{epsfig}

% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
% The amsthm package provides extended theorem environments
% \usepackage{amsthm}
\usepackage{amsmath}

% The lineno packages adds line numbers. Start line numbering with
% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}

% I like to be in control
\usepackage{placeins}

% natbib.sty is loaded by default. However, natbib options can be
% provided with \biboptions{...} command. Following options are
% valid:

%   round  -  round parentheses are used (default)
%   square -  square brackets are used   [option]
%   curly  -  curly braces are used      {option}
%   angle  -  angle brackets are used    <option>
%   semicolon  -  multiple citations separated by semi-colon
%   colon  - same as semicolon, an earlier confusion
%   comma  -  separated by comma
%   numbers-  selects numerical citations
%   super  -  numerical citations as superscripts
%   sort   -  sorts multiple citations according to order in ref. list
%   sort&compress   -  like sort, but also compresses numerical citations
%   compress - compresses without sorting
%
% \biboptions{comma,round}

% \biboptions{}


% Katy Huff addtions
\usepackage{xspace}
\usepackage{color}

\usepackage{multirow}
\usepackage[hyphens]{url}


\usepackage[acronym,toc]{glossaries}
\include{acros}

\makeglossaries

%\journal{Annals of Nuclear Energy}

\begin{document}

%\begin{frontmatter}

% Title, authors and addresses

% use the tnoteref command within \title for footnotes;
% use the tnotetext command for the associated footnote;
% use the fnref command within \author or \address for footnotes;
% use the fntext command for the associated footnote;
% use the corref command within \author for corresponding author footnotes;
% use the cortext command for the associated footnote;
% use the ead command for the email address,
% and the form \ead[url] for the home page:
%
% \title{Title\tnoteref{label1}}
% \tnotetext[label1]{}
% \author{Name\corref{cor1}\fnref{label2}}
% \ead{email address}
% \ead[url]{home page}
% \fntext[label2]{}
% \cortext[cor1]{}
% \address{Address\fnref{label3}}
% \fntext[label3]{}

\title{Modeling and Simulation of Online Reprocessing in the Thorium-Fueled 
        Molten Salt Breeder Reactor\\
\large Response to Review Comments}
\author{Andrei Rykhlevskii, Jin Whan Bae, Kathryn D. Huff}

% use optional labels to link authors explicitly to addresses:
% \author[label1,label2]{<author name>}
% \address[label1]{<address>}
% \address[label2]{<address>}


%\author[uiuc]{Kathryn Huff}
%        \ead{kdhuff@illinois.edu}
%  \address[uiuc]{Department of Nuclear, Plasma, and Radiological Engineering,
%        118 Talbot Laboratory, MC 234, Universicy of Illinois at
%        Urbana-Champaign, Urbana, IL 61801}
%
% \end{frontmatter}
\maketitle
\section*{Review General Response}
We would like to thank the reviewers for their detailed assessment of
this paper. Your suggestions, clarifications, and comments have resulted in 
changes which certainly improved the paper.


\begin{questions}
        \section*{Reviewer 1}

        \question Overall, a well written article in a topic area of interest 
        to a number of audiences. Technically very good, well written in the 
        description and analysis.  Well done authors! 


        A few minor comments/suggestions/clarifications as follows:
        \begin{solution}
                Thank you for these kind comments. Your suggestions have 
                certainly improved the paper. 
        \end{solution}

        %---------------------------------------------------------------------

        \question  Abstract: Given the recent announcement about TransAtomic 
        Power, you may want to remove them from your list?
        \begin{solution}
        		Thank you for your kind review. The current manuscript was submitted before 
		        announcement that TransAtomic is ceasing operations. It is removed from 
                        the list of MSR startups (indeed, the whole list was 
                        removed based on a comment by another reviewer).
        \end{solution}

        %---------------------------------------------------------------------
        \question  Table 1, page 3: SCALE/TRITON is fast as well as thermal 
        reactor capable.  
        \begin{solution}
		        Thank you for the recommendation. In Table 1 ``thermal'' has been changed 
		        to ``thermal/fast''.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 4, Line 48: Should read ``...and refill using a single 
        or multiple unit cell ....''
        \begin{solution}
        		That statement has been modified as requested.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 4, Line 55. Also worth noting that the latest SCALE 
        release will have the same functionality using continuous removal (B. 
        R. Betzler, J. J. Powers, N. R. Brown, and B. T. Rearden, ``Molten Salt 
        Reactor Neutronics Tools in SCALE,'' Proc. M\&C 2017 - International 
        Conference on Mathematics \& Computational Methods Applied to Nuclear 
        Science and Engineering, Jeju, Korea, Apr. 16-20 (2017).)
        \begin{solution}
		        Thank you for the update. This sentence has been added:
        
		        ``The latest SCALE release will also have the same functionality using 
        		truly continuous removals \cite{betzler_implementation_2017}.''
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 8, Fig 2: Appears the image is cut off at the top?
        \begin{solution}
        		The image has been replotted.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 13, line 209: The description of the Pa removal, 
        although correct, isn't quite fully correct. The reason the Pa is 
        removed from the core and hence flux is to then enable the Pa to decay 
        to U233. If it was left in the core, it would transmute further and 
        hence not be able to produce the U233 that is necessary for this 
        breeding cycle to work.
        \begin{solution}
        		``Protactinium presents a challenge, since it has a large absorption cross 
				section in the thermal energy spectrum. Moreover, $^{233}$Pa left in the core
				 would produce $^{234}$Pa and $^{234}$U, neither of which are useful as fuel, 
				 would produce a smaller amount of $^{233}$Pa which decays into the fissile $^{233}$U.
				Accordingly, $^{233}$Pa is continuously removed from the fuel salt into 
				a protactinium decay tank to allow $^{233}$Pa to decay to $^{233}$U 
				without the corresponding negative neutronic impact.''
        \end{solution}

        %---------------------------------------------------------------------
        \question  Table 3: ``cycle time'' is not defined in the paper. Please 
        add.
        \begin{solution}
                        The ``cycle time'' definition has been added at the first 
                        appearance in text. 
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 14, line 224. The 3 day time step as the ``optimum'' for 
        Th fuel cycles in an MSR was first described and concluded by Powers et 
        al. Please add a reference to their initial work.
        \begin{solution}
        		The reference to \cite{powers_new_2013} has been added.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 14, line 234 onwards: Doesn't SERPENT already have an 
        MSR removal capability? If so, what is different about using SaltProc 
        with SERPENT?
        \begin{solution}
                It does. Indeed, much of the inspiration for SaltProc was the 
                lack of documentation, difficulty of use, and various 
                inexplicable results we acquired when we tried use this 
                built-in capability. This capability has not performed well and 
                needs to be better documented and more robustly verified before 
                we can use it. We fully intend to contribute to its improvement 
                if it can be made to agree with expectations.  Additional text 
                to clarify this point has been add to solution for question 
                \ref{built-in}.                
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 18, Figure 7: The figure is hard to interpret or see 
        clearly what is going on. Could an additional figure or a zoomed in 
        portion be added to show what the swing in k is over a much shorter 
        time interval? k seems to be swinging dramatically but over what time 
        period and how would this be controlled in reality? The graph almost 
        suggests that the core is unstable??
        \begin{solution}
                Zoomed portion for 150 EFPD interval has been added. We also 
                added notes on a plot to explain swing in multiplication factor.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 18, line 327: Are those elements removed every 3435 
        days, or is it that the entire salt core is discharged?
        \begin{solution}
		        100 \% of those elements atoms are removed every 3435 
                        days. Full salt discard
		         as it mentioned in Table 3 has not been implemented. More detailed 
		         explanation of this has been added:


                        ``Additionally, the presence of rubidium, strontium, cesium, and barium in the
                        core are disadvantageous to reactor physics.
                        Overall, the effective multiplication factor gradually decreases from 1.075 to
                        $\approx$1.02 at equilibrium after approximately 6 years of irradiation.

                        In fact, SaltProc fully removes
                        all of these elements every 3435 days (not a small mass fraction every 3 days)
                        which causes the multiplication factor to jump by approximately 450
                        pcm, and limits using the batch approach for online reprocessing simulations.
                        In future versions of SaltProc this drawback will be eliminated by removing
                        elements with longer residence times (seminoble metals, volatile fluorides, Rb, Sr,
                         Cs, Ba, Eu). In that approach, chemistry models will inform separation
                         efficiencies for each reprocessing group and removal will optionally be spread more
                         evenly across the cycle time.''
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 19, Figure 8 (and same for Fig 9): y-axis in grams/kgs 
        or mass units would be better for the reader.
        \begin{solution}
                Thank you for the recommendation. Atom density was chosen for 
                publication-to-publication comparison (e.g. Park \emph{et al.} and 
                Betzler \emph{et al.}
                \cite{park_whole_2015, betzler_molten_2017}). Although mass would certainly 
                be more understandable for the reader and will be added in a future releases.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 20, Fig 9: What are the wiggles and dips , especially 
        seen for Np235?
        \begin{solution}
		        Explanation of this phenomenon has been added as follows:

                          ``Small dips in neptunium and plutonium number density 
                          every 16 years are caused by removing $^{237}$Np and 
                          $^{242}$Pu (included in Processing group ``Higher 
                          nuclides'', see Table~3
                          which decays into $^{235}$Np and $^{239}$Pu, 
                          respectively.''
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 20, line 351: It is more than just the Pu isotopes that 
        makes the spectrum harder? What about the other MAs etc?
        \begin{solution}
        		Thank you for the excellent point. The corrected sentence reads thus: 
        
                         ``The neutron energy spectrum at equilibrium is harder 
                         than at startup due to plutonium and other strong 
                         absorbers accumulating in the core during reactor 
                         operation.''
        \end{solution}

        %---------------------------------------------------------------------
        \question  Fig 12: units on y-axis?
        \begin{solution}
                Thanks for catching this. The units $\frac{n}{cm^2 s}$ have been added.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 24, line 389: Should that be ``233U'' and not ``233Th''?
        \begin{solution}
                Yes, we meant $^{233}$U production. The typo has been fixed. 
                Thanks so much for catching it!
        \end{solution}

        %---------------------------------------------------------------------
        \question  Table 5: Please provide some comments on the uncertainties - 
        where do they come from? Also, the ``reference'' results need to state 
        whether ``initial'' or ``equilibrium''
        \begin{solution}
                In Table 5, we added information in the reference column 
                containing data for initial fuel salt composition. Details 
                about uncertainties have been added:

                ``Table 5 summarizes temperature effects on reactivity calculated 
                in this work for both initial and equilibrium fuel 
                compositions, compared with the original \gls{ORNL} report data 
                \cite{robertson_conceptual_1971}.  By propagating the $k_{eff}$  
                statistical error provided by SERPENT2, uncertainty for each 
                temperature coefficient was obtained and appears in Table 5. 
                Other sources of uncertainty are neglected, such as cross 
                section measurement error and approximations inherent in the 
                equations of state providing both the salt and graphite density 
                dependence on temperature.''

        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 26, line 425: ``Relatively large'' compared with what? 
        Perhaps results for an LWR case would be a good basis for comparison?
        \begin{solution}
                The sentence has been extended as follows:
                
                The moderator temperature coefficient (MTC) is positive for the 
                startup composition and decreases during reactor operation 
                because of spectrum hardening with fuel depletion.  Finally, 
                the total temperature coefficient of reactivity is negative for 
                both cases, but decreases during reactor operation due to 
                spectral shift. In summary, even after 20 years of operation 
                the total temperature coefficient of reactivity is relatively 
                large and negative during reactor operation (comparing with 
                conventional PWR which has temperature coefficient about -1.71 
                pcm/$^\circ$F $\approx$ -3.08 pcm/K 
                \cite{forget_integral_2018}), despite positive MTC, and affords 
                excellent reactor stability and control.


        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 27, section 3.8: It needs to be made more clear that 
        these results were calculated, and that they are taken from the code 
        output.
        \begin{solution}
                This has now been clarified in the text:
                
                ``Table~7 summarizes the six factors for both initial and 
                equilibrium fuel salt composition. Using SERPENT2 and SaltProc, 
                these factors and their statistical uncertainties have been 
                calculated for both initial and equilibrium fuel salt 
                composition (see Table~2).''
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 29, Figure 15: Similar comment to above regarding Fig 7 
        - the results are difficult to see and interpret with such notable 
        swings.
        \begin{solution}
                Zoomed portion for 150 EFPD interval has been added along with 
        clarifying details.
        \end{solution}

        %---------------------------------------------------------------------




        \section*{Reviewer 2}

        %---------------------------------------------------------------------
        \question The paper presents a python script (SaltProc) that can 
        complement the Serpent 2 code capabilities in terms of fuel cycle 
        analysis of MSRs. The paper is well written and the tool might be 
        useful for the nuclear engineering community. However, before 
        publishing the paper, I recommend some revisions.
        \begin{solution}
                Thanks very much for these comments. We appreciate your 
                detailed review, which has certainly improved the paper.
        \end{solution}

        %---------------------------------------------------------------------

        \question \label{built-in} The most critical point of the work is that the built-in 
        capabilities for online reprocessing of Serpent 2 have not been used. 
        Their use is mentioned in the future work, but it is not clear why 
        these capabilities have not been used in the current work. To the 
        author's knowledge, they have been available in Serpent 2 since quite a 
        while. The authors should clarify this point at the beginning of the 
        paper, and not only in the ``Future work'' section. Even though the 
        technical work was done without using these capabilities, they should 
        highlight what  SaltProc adds to the built-in Serpent capabilities, and 
        they should at least try to extrapolate on the potential advantages of 
        combining  SaltProc and Serpent capabilities. Based on this, they 
        should slightly restructure the paper in order to prove the claimed 
        advantages over Serpent 2.
        \begin{solution}
                Thank you for your helpful review. We tried to use these capabilities 
                \cite{rykhlevskii_online_2017} but have had a number of issues which 
                are hard to resolve due to lack of documentation and 
                published verifications of this feature. The following 
                paragraph has been added to clarify why these capabilities have 
                not been used in current work:
                
                
                ``Aufiero \emph{et al.} added an undocumented feature to SERPENT2 
                using a similar methodology by explicitly introducing 
                continuous reprocessing in the system of Bateman equations and 
                adding effective decay and transmutation terms for each nuclide 
                \cite{aufiero_extended_2013}. This was employed to study the 
                material isotopic evolution of the 
                \gls{MSFR}\cite{aufiero_extended_2013}. The developed extension 
                directly accounts for the effects of online fuel reprocessing 
                on depletion calculations and features a reactivity control 
                algorithm. The extended version of SERPENT2 was assessed 
                against a dedicated version of the deterministic ERANOS-based 
                EQL3D procedure in \cite{ruggieri_eranos_2006, 
                fiorina_investigation_2013} and adopted to analyze the 
                \gls{MSFR} fuel salt isotopic evolution.
                
                We employed this built-in SERPENT2 feature for a simplified 
                unit-cell geometry of the thermal spectrum thorium-fueled 
                \gls{MSBR} and found it unusable\footnote{ Some challenges in 
                no particular order: mass conservation is hard to achieve; 
                three types of mflow cards (0, 1 or 2) are indistinguishable in 
                purpose; an unexplained difference between CRAM and TTA 
                results; etc.}. Primarily, it is undocumented, and the 
                discussion forum for SERPENT users is the only useful source of 
                information at the moment. Additionally, the reactivity control 
                module described in Aufiero \emph{et al.} is not available in 
                the latest SERPENT 2.1.30 release. Third, the infinite 
                multiplication factor behavior for simplified unit-cell model 
                obtained using SERPENT2 built-in capabilities 
                \cite{rykhlevskii_online_2017} does not match with exist 
                MCNP6/Python-script results for the similar model by Jeong and 
                Park\footnote{ In our study k$_{\infty}$ drops from 1.05 to 
                1.005 during a 1200 days of depletion simulation while in Jeong 
                and Park work this parameter decreasing slowly from 1.065 to 
                1.05 for the similar time-frame.} 
                \cite{jeong_equilibrium_2016}. Finally, only two publications 
                \cite{aufiero_extended_2013, ashraf_nuclear_2018} using these 
                capabilities are available, reflecting the reproducibility 
                challenge inherent in this feature.
                
                If these challenges can be overcome through verification 
                against ChemTriton/SCALE as well as this work (the 
                SaltProc/SERPENT2 package), we hope to employ this SERPENT2 
                feature for removal of fission products with shorter residence 
                time (e.g., Xe, Kr), since these have a strong negative impact 
                on core lifetime and breeding efficiency.''

        \end{solution}

        %---------------------------------------------------------------------

        \question In addition to this major point, I would suggest a few other 
        revisions. Considering the scope of the journal, mentioning the names of 
        companies and start-up is not appropriate. I would suggest removing 
        them.
        \begin{solution}
                The names of companies have been removed.
        \end{solution}

        %---------------------------------------------------------------------
        
        \question The sentence ``Immediate advantages over traditional, solid-fueled, 
        reactors include near-atmospheric pressure in the 15 primary loop, 
        relatively high coolant temperature, outstanding neutron economy, 
        improved safety parameters,'' may suggest improved neutron economy vs 
        solid-fuel fast reactors. This is rarely the case, especially vs 
        Pu-based SFRs. I would suggest reformulating.
        \begin{solution}
                Thank you for the exceptional recommendation. The sentence has 
                been split into two, as follows:

                Immediate advantages over traditional commercial reactors 
                include near-atmospheric pressure in the primary loop, 
                relatively high coolant temperature, outstanding neutron 
                economy, and improved safety parameters. Advantages over 
                solid-fueled reactors in general include reduced fuel 
                preprocessing and the ability to continuously remove fission 
                products and add fissile and/or fertile elements 
                \cite{leblanc_molten_2010}.

        \end{solution}

        %---------------------------------------------------------------------

        \question The sentence ``With regard to the nuclear fuel cycle, the 
        thorium cycle produces a reduced quantity of plutonium and minor 
        actinides (MAs) compared to the traditional uranium fuel cycle'' is 
        correct, but the fact that this is an advantage is questionable. The 
        pros\&cons of thorium cycle have been long debated and there is no 
        consensus on its advantage in terms of exposure of workers, exposure of 
        public, geological repository, etc. I would suggest removing the 
        sentence.
        \begin{solution}
                Thanks for your insightful comment. The sentence has been removed.
        \end{solution}

        %---------------------------------------------------------------------


        \question ``Methods listed in references [14, 17, 24, 25, 28, 29, 30] 
        as well as the current work also employ a batch-wise approach''. As a 
        matter of fact, the work in [14]  allows for continuous reprocessing 
        via introduction of ``reprocessing'' time constants. The work from  
        Aufiero (mentioned in the following paragraph) actually used the 
        methodology previously developed in [14]  for verification purposes.
        \begin{solution}
                Thank you for the information. That reference has been removed from the 
                sentence, and following paragraph has been modified to read:
                
                
                Accounting for continuous removal or addition presents a 
                greater challenge since it requires adding a term to the 
                Bateman equations. Fiorina \emph{et al.} simulated \gls{MSFR} 
                depletion with continuous fuel salt reprocessing via 
                introducing ``reprocessing'' time constants into the ERANOS 
                transport code \cite{fiorina_investigation_2013}.  The latest 
                SCALE release will also have the same functionality using truly 
                continuous removals \cite{betzler_implementation_2017}.  A 
                similar approach is adopted to model true continuous feeds and 
                removals using the MCNP transport code listed in references 
                \cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.

                
        \end{solution}

        %---------------------------------------------------------------------

        \question Table 3. It is not clear what ``effective cycle times'' are. 
        Please clarify.
        \begin{solution}
                The ``cycle time'' definition has been added to its first appearance in text.
        \end{solution}

        %---------------------------------------------------------------------

        \question The removal of fission products is made batch wise in the 
        described algorithms. However it is not clear how the fission products 
        with the longest ``effective cycle times'' are removed. Part of them at 
        every batch? Or all of them at the end of the  ``effective cycle 
        times''.  Please clarify. And please clarify the relation between 
        ``effective cycle times'', batches and the average time spent by a 
        fission product in the reactor.
        \begin{solution}
                All of them at the end of the cycle time, and we agree that it
                 was not best solution. Feature improvements in SaltProc are 
                 underway to enable more realistic handling times in the 
                 processing heuristics. To clarify this following paragraph has 
                been added:
                
                The current version of SaltProc only allows 100\% separation 
                efficiency for either specific elements or groups of elements 
                (e.g. Processing Groups as described in 
				Table~\ref{tab:reprocessing_list}) at the end of the specific 
				cycle time. This simplification neglects the reality that 
				the salt spends appreciable time out of the core, in the 
				primary loop pipes and the heat exchanger.  

				This approach works well for fast-removing elements (gases, 
				noble metals, protactinium) which should be removed each 
				depletion step. Unfortunately, for the elements with longer 
				cycle times (i.e. rare earths should be removed every 50 days) 
				this simplified approach leads to oscillatory behavior of all
				major parameters. In future releases of SaltProc, this drawback 
				will be eliminated by removing elements with longer cycle times 
				using different method: only mass fraction (calculated separately 
				for each reprocessing group) will be removed each depletion step 
				or batch (e.g. 3 days in the current work).
        \end{solution}

        %---------------------------------------------------------------------

        \question \label{osc} The oscillatory behavior shown in Fig. 7 on the time scale of 
        months/years is hard to explain. Is this because the fission product 
        with longer residence time are batch-wise removed at their ``effective 
        cycle time''? In case, why not to remove part of them at every depletion 
        step?  
        \begin{solution}
                Yes, the oscillation happened because the fission products 
                with longer residence time are removed at the end of cycle time. We 
                definitely will take your advice and improve the code in future 
                releases. The following text has been added to clarify this issue:
                
                In fact, SaltProc fully removes all of these elements every 
                3435 days (not a small mass fraction every 3 days) which causes 
                the multiplication factor to jump by approximately 450 pcm, and 
                limits using the batch approach for online reprocessing 
                simulations.  In future versions of SaltProc this drawback will 
                be eliminated by removing elements with longer residence times 
                (seminoble metals, volatile fluorides, Rb, Sr, Cs, Ba, Eu). In 
                that approach, chemistry models will inform separation 
                efficiencies for each reprocessing group and removal will 
                optionally be spread more evenly accross the cycle time.


        \end{solution}

        %---------------------------------------------------------------------

        \question Can the proposed tool adjust reactivity?
        \begin{solution}
                No, and we may someday add this capability, but we expect this 
                will be a challenge outside of the depletion code.
        \end{solution}

        %---------------------------------------------------------------------

        \question ``The main physical principle underlying the reactor 
        temperature feedback is an expansion of material that is heated''. This 
        sentence would deserve some support data. Can you please calculate 
        separately the effect of temperature (Doppler in fuel and spectral 
        shift in graphite) and density?
        \begin{solution}
                Thank you for the excellent recommendation. Effects of temperature
                 and density have been calculated separately and added in Table 5.
                 Moreover, during these simulations we have discovered mistake in 
                 fuel salt and graphite density correlations and completely 
                 recalculated temperature coefficients of reactivity with lower 
                 statistical error. Now initial total temperature coefficient is 
                 closer to the reference and statistical uncertainty was reduced 
                 from 0.046 to 0.038 pcm/K.
        \end{solution}

        %---------------------------------------------------------------------

        \question How uncertainties have been calculated in Table 5? Is this 
        just statistical uncertainty from Serpent calculations? Please clarify
        \begin{solution}
                Yes, uncertainties were determined from statistical error 
                from SERPENT output. Following passage has been added to clarify
                 this point:
                 
                 By propagating the $k_{eff}$  statistical error provided by 
                 SERPENT2, uncertainty for each temperature coefficient was 
                 obtained and appears in Table~\ref{tab:tcoef}. Other sources 
                 of uncertainty are neglected, such as cross section 
                 measurement error and approximations inherent in the equations 
                 of state providing both the salt and graphite density 
                 dependence on temperature.  
        \end{solution}

        %---------------------------------------------------------------------

        \question For calculating the coefficients in table 5, are you only 
        changing densities, or also dimensions? Please clarify and provide a 
        justification.  
        \begin{solution}
        		We have changed both densities and dimensions. This passage 
        		has been modified to read:

                        A new geometry input for SERPENT2, which takes into 
                        account displacement of graphite surfaces, was created 
                        based on this information. For calculation of 
                        displacement, it was assumed that the interface between 
                        the graphite reflector and vessel did not move, and 
                        that the vessel temperature did not change. This is the 
                        most reasonable assumption for the short-term 
                        reactivity effects because inlet salt is cooling 
                        graphite reflector and inner surface of the vessel.

        \end{solution}

        %---------------------------------------------------------------------

        \question ``The fuel temperature coefficient (FTC) is negative for both 
        initial and equilibrium fuel compositions due to thermal Doppler 
        broadening of the resonance capture cross sections in the thorium.'' 
        What is the effect of density?
        \begin{solution}
                This passage has been modified to illuminate the effect of density:
                
                The fuel temperature coefficient (FTC) is negative for both 
                initial and equilibrium fuel compositions due to thermal 
                Doppler broadening of the resonance capture cross sections in 
                the thorium. A small positive effect of fuel density on 
                reactivity increases from $+1.21$ pcm/K at reactor startup to 
                $+1.66$ pcm/K for equilibrium fuel composition which has 
                a negative effect on FTC magnitude during the reactor operation. 
        \end{solution}

        %---------------------------------------------------------------------

        \question ``This thorium consumption rate is in good agreement with a 
        recent online reprocessing study by ORNL [29].'' Please notice that in a 
        reactor with only Th as feed, and near equilibrium, the Th consumption 
        rate is  exclusively determined by the reactor power and by the energy 
        released per fission.  
        \begin{solution}
                Thank you for the recommendation. Following sentence has been 
                added:
                
                It must be noted that for the reactor with only thorium feed, 
                at near equilibrium state, the thorium consumption rate is 
				determined by the reactor power, the energy released per fission, 
				and neutron energy spectrum.
        \end{solution}

        %---------------------------------------------------------------------

        \question Are you considering the effect of the gradual poisoning of 
        the graphite with fission products? If not, it would be worthwhile 
        briefly discussing its effect.
        \begin{solution}
                This passage has been added:
				
				$^{135}$Xe is a strong poison to the reactor, and some 
				fraction of this gas is absorbed by graphite during MSBR
				operation. ORNL calculations shown that for unsealed commercial 
				graphite with helium permeability 10$^{-5}$ cm$^2$/s the 
				calculated poison fraction is less than 2\% \cite{robertson_conceptual_1971}. 
				This parameter can be improved by using experimental graphites 
				or by applying sealing technology. The effect of the gradual 
				poisoning of the core graphite with xenon is not treated here.
        \end{solution}

        %---------------------------------------------------------------------

        \question In the manuscript it is not always clear when the authors 
        refer to numerical approximations of physical situations. For instance, 
        the authors write ``Figure 16 demonstrates that batch-wise removal of 
        strong absorbers every 3 days did not necessarily leads to fluctuation 
        in results but rare earth elements 480 removal every 50 days causes an 
        approximately 600 pcm jump in reactivity.'' These 600 pcm are an effect 
        of a numerical approximation, but the way things are presented can be 
        confusing to the reader. Please try to explicitly separate physical and 
        numerical effects. And try to related numerical effects to physical 
        effects. For instance, how does these numerical ``jumps'' affect the 
        results?  In this sense, why the batch-wise removal of strong absorbers 
        every 3 days  was not done? And why a fraction of rare earths  is not 
        removed every three days?
        \begin{solution}
                This sentence was quite unclear and we have rewritten it to 
                address your concerns. Effectively these simulations exactly 
                simulated the batch-wise refuelling detailed in the Robertson 
                design document, while a more realistic approach would give 
                smooth behavior. A description of the changes to the text 
                appears in solution \ref{osc}.
        \end{solution}

        %---------------------------------------------------------------------



        \question ``The current work results show that a true equilibrium 
        composition cannot exist but balance between strong absorber 
        accumulation and new fissile material production can be achieved to 
        keep the reactor critical.'' Not clear. Do you mean that the equilibrium 
        composition cannot be achieved in a lifetime of the reactor? Please 
        clarify
        \begin{solution}
                This statement, being unclear and misleading, has been removed 
                completely. The intention was to communicate that for a relaxed 
                definition of equillibrium, it can be acheived.
        \end{solution}

        %---------------------------------------------------------------------



        \section*{Reviewer 3}

        \question This paper presents a SaltProc-Serpent2 coupled code system
        to simulate the depletion and online reprocessing process by directly
        changing the isotropic composition of fuel salt. The Molten Salt
        Breeder Reactor (MSBR) was analyzed to demonstrate the simulation
        capability of the developed code system. However, large number of
        similar works have been done and published on this topic. In
        particular, this work is similar with that done by Park et al. with the
        title of ``Whole core analysis of molten salt breeder reactor with
        online fuel reprocessing'' published on ``International Journal of Energy
        Research''. The authors need to prove the uniqueness and innovation
        within their work.
        \begin{solution}
                We appreciate this comment and have made clarifying 
                improvements to indicate the impact of this work throughout the 
                paper. More detail is described regarding these changes in the 
                specific comment responses below.
        \end{solution}

        %--------------------------------------------------------------------

        \question  What are the main differences of this work with the previous 
        works, especially with the work published by Park at al. in ``Whole core 
        analysis of molten salt breeder reactor with online fuel reprocessing''?
        \begin{solution}
                Thank you for your question. The new paragraph has been added:

                The works described in \cite{park_whole_2015} and 
                \cite{jeong_equilibrium_2016} are most similar to the work 
                presented in this paper. However, a few major differences 
                follow: (1) Park \emph{et al.} employed MCNP6 for depletion 
                simulations while this work used SERPENT2; (2) the full-core 
                reactor geometry herein is more detailed 
                \cite{rykhlevskii_full-core_2017}; (3) Park \emph{et al.} and 
                Jeong \emph{et al.} both only considered volatile gas removal, 
                noble metal removal, and $^{233}$Pa separation while the 
                current work implemented the more detailed reprocessing scheme 
                specified in the conceptual \gls{MSBR} design 
                \cite{robertson_conceptual_1971}; (4) the $^{232}$Th neutron 
                capture reaction rate has been investigated to prove advantages 
                of two-region core design; (5) the current work explicitly 
                examines the independent impacts of removing specific fission 
                product groups.
        \end{solution}

        %--------------------------------------------------------------------
        \question  How did the authors verify the coupled SaltProc and Serpent 
        code system?  
        \begin{solution}
                We have compared few parameters (multiplication factor, Th refill 
                rate, neutron energy spectrum) with Betzler \emph{et al.} 										
                \cite{betzler_molten_2017} and mentioned it in the Result section. 
                We also compared neutron energy spectrum and temperature coefficients
                 for equilibrium composition with Park \emph{et al.} \cite{park_whole_2015}.
                In a future SaltProc release suite of unit tests will be added 
                to make sure that results are consistent with our test cases.
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 3, the title of ``Table 1'' should not only contain 
        the ``fast spectrum system''. The work published by Zhou and Yang et al. 
        with the title of ``Fuel cycle analysis of molten salt reactors based on 
        coupled neutronics and thermal-hydraulics calculations'' needs to be 
        included in Table 1 for completeness.
        \begin{solution}
                Thank you for your excellent recommendations. The table has been 
                enriched as requested.
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 5, the following sentence needs to be explained. ``We 
        employed this extended SERPENT 2 for a simplified unit-cell geometry of 
        thermal spectrum thorium-fueled MSBR and obtained results which 
        contradict existing MSBR depletion simulations.''
        \begin{solution}
                This statement has been significantly extended (see solution 
                \ref{built-in}).
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 10, ``SERPENT generates the problem-dependent nuclear 
        data library'', how did SERPENT generate the problem-dependent nuclear 
        data library? What kind of nuclear data library did SERPENT generate?
        \begin{solution}
                Thank you for your kind review. The statement has been removed
		        entirely and we emphasized that temperature of each material is 
		        assumed to be constant over 60 years:
		        
		        The specific temperature was fixed for each material and did 
		        not change during the reactor operation. 
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 14, ``depletioncalculations'' should be ``depletion 
        calculations''.
        \begin{solution}
                Thanks for catching this, fixed.
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 21, it looks like the neutron spectrum is not 
        normalized in Figure 10. It is recommended to normalize the neutron 
        spectrum for comparison.
        \begin{solution}
                Thank you for the comment. Neutron energy spectrum in Figure 
                10 and 11 are normalized per unit lethargy and the area under 
                the curve is normalized to 1. The caption has been edited to 
                make this more clear.
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 22, ``Figure 13 reflects the normalized power 
        distribution of the MSBR quarter core, which is the same at both the 
        initial and equilibrium states'' contradicts the following statement of 
        ``The spectral shift during reactor operation results in different power 
        fractions at startup and equilibrium''.
        \begin{solution}
                Thanks for catching this. The difference between power fraction
                 is very small that could be seen from Table 4. It is impossible
                  to see the difference in a contour plot that is why we left only 
                 equilibrium composition on Figures 13 and 14. The paragraph has 
                 been modified as follows:
                 
                 Table~4 shows the power fraction in each zone for initial and 
                 equilibrium fuel compositions. Figure~13 reflects the 
                 normalized power distribution of the \gls{MSBR} quarter core 
                 for equilibrium fuel salt composition. For both the initial 
                 and equilibrium compositions, fission primarily occurs in the 
                 center of the core, namely zone I. The spectral shift during 
                 reactor operation results in slightly different power 
                 fractions at startup and equilibrium, but most of the power is 
                 still generated in zone I at equilibrium (table~4).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
                   
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 24, it is hard to agree with the statement that ``the 
        majority of 233Th is produced in zone II.''. How did the authors draw 
        this conclusion?
        \begin{solution}
                The statement has been removed entirely.
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 24 and 25, why did the normalized power density 
        distribution and the 232Th neutron capture reaction rate distribution 
        share the same figure for both initial and equilibrium fuel salt 
        compositions?
        \begin{solution}
                Thanks for catching this, it is a typo. Figure 13 and 14 are plotted 
                for equilibrium composition only.            	    
        \end{solution}

        %--------------------------------------------------------------------
        \question  Too much background information was contained in the 
        abstract, which deteriorates the readability of the abstract.
        \begin{solution}
                The abstract has been shortened.
        \end{solution}

        %--------------------------------------------------------------------
\end{questions}
\bibliographystyle{unsrt}
\bibliography{../2018-msbr-reproc}
\end{document}

%
% End of file `elsarticle-template-num.tex'.
